\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-09 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
adding IEEE 14 bus sim results

@@

\author{Abhishek~Halder,~\IEEEmembership{Senior Member,~IEEE,} 
%\author{Abhishek~Halder,~\IEEEmembership{Member,~IEEE,}
        Kenneth~F. Caluya,
        Pegah~Ojaghi,
        and~Xinbo~Geng,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{A. Halder and K.F. Caluya are with the Department of Applied Mathematics, University of California, Santa Cruz, CA 95064, USA, {\texttt{\{ahalder,kcaluya\}@ucsc.edu}}.}% <-this % stops a space
\thanks{X. Geng is with the School of Electrical and Computer Engineering, Cornell University, Ithaca, NY 14850, USA, {\texttt{xg72@cornell.edu}}.} %
\thanks{P. Ojaghi is with the Department of Computer Science and Engineering, University of California, Santa Cruz, CA 95064, USA, {\texttt{pojaghi@ucsc.edu}}.}%
\thanks{This research was partially supported by the NSF award 1923278.}}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%

@@

\subsection{IEEE 14 Bus System}\label{subsec:NumSimIEEEBus}
Following Sec. \ref{subsec:samplepathdynamics}, we consider the Kron-reduced dynamics \eqref{ItoSDEcomponentlevel} for the IEEE 14 bus system shown in Fig. \ref{fig:Motivating}. In this case, we have $n=5$ nodes which correspond to the buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. {\red{The parameter values in \eqref{DefParam} use the network reduced admittance matrix computed from the CITE?? The parameters $m_{i}, \gamma_{i}$ are obtained from ....}} We randomly generated $\sigma_{i}\in [1,5]$ as
\[(\sigma_{1},\hdots,\sigma_5) = \left(2.4628, 4.9266, 4.8724, 1.4215, 3.8681\right).\]

@@

>>>>

%\begin{document}
%
%\title{\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions}
%
%\author{Abhishek~Halder,~\IEEEmembership{Senior Member,~IEEE,} 
%%\author{Abhishek~Halder,~\IEEEmembership{Member,~IEEE,}
%        Kenneth~F. Caluya,
%        Pegah~Ojaghi,
%        and~Xinbo~Geng,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
%\thanks{A. Halder and K.F. Caluya are with the Department of Applied Mathematics, University of California, Santa Cruz, CA 95064, USA, {\texttt{\{ahalder,kcaluya\}@ucsc.edu}}.}% <-this % stops a space
%=======

@@

\author{Abhishek~Halder,~\IEEEmembership{Senior Member,~IEEE,} 
        Kenneth~F. Caluya,
        Pegah~Ojaghi,
        and~Xinbo~Geng,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{A. Halder and K.F. Caluya are with the Department of Applied Mathematics, University of California, Santa Cruz, CA 95064, USA, {\texttt{\{ahalder,kcaluya\}@ucsc.edu}}.}% <-this % stops a space
\thanks{P. Ojaghi is with the Department of Computer Science and Engineering, University of California, Santa Cruz, CA 95064, USA, {\texttt{pojaghi@ucsc.edu}}.}%
\thanks{X. Geng is with the School of Electrical and Computer Engineering, Cornell University, Ithaca, NY 14850, USA, {\texttt{xg72@cornell.edu}}.} %
\thanks{This research was partially supported by the NSF award 1923278.}}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%

@@

\subsection{IEEE 14 Bus System}\label{subsec:NumSimIEEEBus}
We consider the Kron-reduced dynamics \eqref{ItoSDEcomponentlevel} for the IEEE 14 bus system shown in Fig. \ref{fig:Motivating}. In this case, we have $n=5$ nodes which correspond to the buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. We obtained the parameters of the 14 bus system from MATPOWER \cite{zimmerman2010matpower}. The calculation of Kron-reduced admittance matrix and current vector in \eqref{DefParam} followed Sec.  \ref{subsec:samplepathdynamics}; see also \cite{dorfler2012kron}. The parameters $m_{i}, \gamma_{i}$ are obtained from the open-source Python-based
library ANDES \cite{cui2021andes}.

We randomly generated the noise coefficients $\sigma_{i}\in [1,5]$ as
\[(\sigma_{1},\hdots,\sigma_5) = \left(2.4628, 4.9266, 4.8724, 1.4215, 3.8681\right).\]

@@

\bibitem{zimmerman2010matpower}
R.D.~Zimmerman, C.E.~Murillo-S{\'a}nchez, and R.J. Thomas, ``MATPOWER: Steady-state Operations, Planning, and Analysis Tools for Power Systems Research and Education'', \emph{IEEE Transactions on Power Systems},  Vol. 26, No. 1, pp. 12--19, 2010.

\bibitem{cui2021andes}
H.~Cui, F.~Li, and K.~Tomsovic, ``Hybrid Symbolic-Numeric Framework for Power System Modeling and Analysis,'' \emph{IEEE Transactions on Power Systems}, vol. 36, no. 2, pp. 1373-1384, 2021.
